The Privacy of Private Browsing

### 2013-12-15 finalproject/paper.tex
edits all over the place
almost done (need to re-export pdf and clean up)

    %\subsection{Browser Extensions}
    % Write me!

@@

  Until Mozilla, Google, and Microsoft reduce the artifacts leaker by their
  respective browsers' private modes, users who are concerned about ``local 
  attackers''---those of the nosy roommate or family member variety who have 
  physical access to their machine---can do their part to keep their private
  information secure. Random access memory, where private browsing artifacts
  have been found, is cleared when a computer is powered down. Shutting down
  the computer after a private browsing session can reduce or eliminate these
  artifacts. Hard drive artifacts, however, are nearly impossible to eradicate.
  The moral of the story is that private browsing is nothing more than a nice
  illusion useful for fooling the computer-illiterate. At the end of the day,
  private browsing really isn't that private at all.

>>>>

	\subsection{Proof of Concept: Parsing SQLite Databases and Browser Memory}
	% find paper that had the thing about no last visited date and cite
	As an example of the persistence of some of these private browsing 
	shortcomings, two Python scripts were written to accompany this paper.
	The first parses the SQLite databases of Mozilla Firefox to look for 
	private browsing artifacts. There are two built-in artifact searches. It 
	will print any cookies created within the last hour; if private browsing is
	currently in use, some cookies may show up here before being removed upon
	browser termination. Additionally, URLs that have a nonzero access count
	but an unspecified last visit time will be printed. It cannot be easily
	determined when these websites were visited, but it is likely that it was
	during a private browsing session. Upon manual review of the URLs retrieved 
	from this database, URLs visited more recently during a private browsing 
	session appeared at the bottom of the list. The 
	\href{https://addons.mozilla.org/en-US/firefox/addon/sqlite-manager}
	{SQLite Manager} extension for Firefox was used to discover these possible
	artifact sources before a programmatic solution was implemented.

	The second script retrieves the contents of the memory segments associated
	with a running Firefox or Chrome process.
	%Finish this

@@

  Until Mozilla, Google, and Microsoft reduce the artifacts leaker by their
  respective browsers' private modes, users who are concerned about ``local 
  attackers''---those of the nosy roommate or family member variety who have 
  physical access to their machine---can do their part to keep their private
  information secure. Random access memory, where private browsing artifacts
  have been found, is cleared when a computer is powered down. Shutting down
  the computer after a private browsing session can reduce or eliminate these
  artifacts. Hard drive artifacts, however, are nearly impossible to eradicate.
  Even if the files whose timestamps were updated upon termination of a 
  private browsing session could be deleted without affecting the browser, 
  their fragments would still remain on the hard drive. The moral of the story 
  is that private browsing is nothing more than a nice illusion useful for 
  fooling the computer-illiterate. At the end of the day, private browsing 
  really isn't that private at all.
